

# By Year 



## Row 1 {data-height=150} 

Note the data visualized here is taken from web sources listed in the tab below.

```{r}

renderText ({
  if (id1() != 83 ) {
    cat ("Not enough data for selected Department.\n Please see evailable data sources in the tab below and submit addtional data to developer, should you wish these data be added to the Application.")
  }   else {
       cat ("Note the data visualized here is taken from web sources listed in the tab below") 
  }
})

renderUI({
  if (id1() == 83 ) {
    selectInput('organizationSED', 'Select Department(s) (click DEL to remove):',
                # choices = c("All", dtSED$Organization %>% unique()),
                # selected="All", #(dtSED$Organization %>% unique()),
                choices = c(dtSED$Organization %>% unique()),
                width="100%",
                selected=c(dtSED$Organization %>% unique())[c(1,2,5)],
                multiple=T
    )
    
    # selectInput('themeSED', 'Select theme:',
    #             choices = c("All", dtSED$Theme %>% unique()), width="100%",
    #             selected="All")
    #             
        selectInput('questionSED', 
                'Select Question:', 
                # 'Select upto 4 Questions:', 
                width="100%", 
                selectize = F,size=5,
                choices = c(dtSED$strQuestion %>% unique())
    ) 
    

    
  }
})


```


## Row 2 {.tabset .tabset-fade}

### Score by Year  {data-height=600} 



```{r psesSED.plotQuestionByTime_lines}
renderPlot({
  
      dtSED0 <- reactive({
      dtSED[strQuestion %in% input$questionSED &
                  Organization %in% input$organizationSED,
              # LEVEL <= r.myLevel(),
              c(1:11, ncol(dtSED)),with=F]
    })
    
  
  if (id1() == 83 ) {
    psesSED.plotQuestionByTime_lines(dtSED0(), input$questionSED);
  }
})
```




### Tabular view


```{r}
DT::renderDataTable({
  
  if (id1() == 83 ) {
    data <- dtSED0()
    DT::datatable(data, options = list(
      bPaginate = FALSE
      #    pageLength = 10
    ))
  }
})
# renderTable({
#   dtSED0()
# })
```




### Sources


- 2018 Public Service Employee Survey Results by Theme for Science and Engineering:    
[www.tbs-sct.gc.ca/pses-saff/2018/results-resultats/bq-pq/83/200/304/418/org-eng.aspx]({data-height=50} )
- 2017 Public Service Employee Survey Results for SCIENCE AND ENGINEERING:    
[www.tbs-sct.gc.ca/pses-saff/2017-2/results-resultats/bq-pq/83/002/022/026/org-eng.aspx]()
- 2014 Public Service Employee Survey Results by Question for Science and Engineering:   
[www.tbs-sct.gc.ca/pses-saff/2014/results-resultats/bq-pq/83/001/250/255/org-eng.aspx]()
- 2011 Public Service Employee Survey Organizational Results: Science and Engineering:   
[www.tbs-sct.gc.ca/pses-saff/2011/results-resultats/bq-pq/83/090/400/403/org-eng.aspx]()


