


# By Year



## Row  {.tabset .tabset-fade}

Not enough data for selected Department.  Please contact the developer.

### Score by Question {data-height=600} 

```{r}

renderPlot({
  
  setkeyv(dtDepartments,PSES_ID_COLS)
  dtRESULT <<- 
        dtPSES[ # All SURVEYR
    # dtPSES[SURVEYR %in% input$year][
    r.DeptSelected(), on=PSES_ID_COLS][
      dtQuestions, on="QUESTION"]
  
  setkeyv(dtRESULT, PSES_ID_COLS)
  #q <- (dtRESULT$QUESTION %>% unique)[2];q
  for (q in dtRESULT$QUESTION %>% unique) {
    myScore <- dtRESULT[as.list(myID)][QUESTION==q]$SCORE100; myScore
    myRank <- dtPSES[QUESTION==q &  SCORE100 > myScore, .N] ; myRank
    dtRESULT[QUESTION==q, ':=' (
      RANK=dtPSES[QUESTION==q & LEVEL1ID > 0 &  SCORE100 > myScore, .N],
      TOTAL=dtPSES[QUESTION==q & LEVEL1ID > 0, .N]       )
      ] [, RANK100:=round(RANK/TOTAL*100)]
    dtRESULT[QUESTION==q & IDlevel == 0, ':=' (RANK100=50)]
  }
  
  
  Questions_vs_Scores(input) +
    
    labs(
      title=paste(input$year, "Public Service Employee Survey Results"), 
      subtitle=paste0("Department: ",
                      # "Department:", dtDepartments[as.list(myID)]$pathString, 
                      dtDepartments[as.list(myID)]$Organization,
                      " (Ranking percentile is indicated in the box, Public Service average is marked by cross)")
    ) 
})
```

### Tabular view {data-height=600} 


#### Department:
```{r}

renderText({
  dt <- dtDepartments[ as.list(c(id1(),id2(),id3(),id4(),id5() ) )]
  #   dt <- dtDepartments[ .(c(id1(),id2(),id3(),id4(),id5() ) )]
  sprintf("Level: %i. %s (%s, ID=%i.%i.%i.%.i.%i)" , 
          dt$IDlevel, dt$Organization, dt$AADD, 
          id1(),id2(),id3(),id4(),id5())
})
```

#### Responses:
```{r}

DT::renderDataTable({
  
  # dt <- getResultsParents (id=c(id1(),id2(),id3(),id4(),id5()),
  #                          nQ = dtQuestions[Theme %in% input$theme]$QUESTION,
  #                          aYears=input$year) 
  
  DT::datatable(
    #r.dtAll(),
    dtRESULT[, .(SURVEYR,QUESTION,IDlevel, pathString,SCORE100,ANSCOUNT)],
    options = list(
      bPaginate = T,
      pageLength = 10
    ))
})

```




### Sources


- 2018 Public Service Employee Survey Results by Theme
<!-- for Science and Engineering:    -->
[www.tbs-sct.gc.ca/pses-saff/2018/results-resultats/bq-pq/83/200/304/418/org-eng.aspx]({data-height=50} )
- 2017 Public Service Employee Survey Results 
<!-- for SCIENCE AND ENGINEERING:     -->
[www.tbs-sct.gc.ca/pses-saff/2017-2/results-resultats/bq-pq/83/002/022/026/org-eng.aspx]()
- 2014 Public Service Employee Survey Results by Question 
<!-- for Science and Engineering:    -->
[www.tbs-sct.gc.ca/pses-saff/2014/results-resultats/bq-pq/83/001/250/255/org-eng.aspx]()
- 2011 Public Service Employee Survey Organizational Results: 
<!-- Science and Engineering:    -->
[www.tbs-sct.gc.ca/pses-saff/2011/results-resultats/bq-pq/83/090/400/403/org-eng.aspx]()


