

<!-- # Analyze interactively -->
# Compare by Years


## Row   {data-height=400}

<!-- {data-height=500}  -->

<!-- {.tabset .tabset-fade} -->



### Make Selection


```{r}

selectInput('organizationSED', 'Select Department(s) (click DEL to remove):', 
            # choices = c("All", dtSED$Organization %>% unique()), 
            # selected="All", #(dtSED$Organization %>% unique()), 
            choices = c(dtSED$Organization %>% unique() ), 
            width="100%",
            selected=c(dtSED$Organization %>% unique())[c(1,2,5)], 
            multiple=T 
) 

# selectInput('themeSED', 'Select theme:',
#             choices = c("All", dtSED$Theme %>% unique()), width="100%",
#             selected="All")


if (T) {
  selectInput('questionSED', 'Select Question:', 
              width="100%", 
              selectize = F,size=10,
              choices = c(dtSED$strQuestion %>% unique() %>% sort(decreasing=F))
  ) 
  #strQuestions, width="100%") 
}else {
  
  dtSED.subset<- reactive({
    if (input$theme=="All") {
      dtSED
    }else{
      dtSED[Theme == input$themeSED]
      #     dtSED %>% dplyr::filter(Theme==input$Zone)
    }
  })
  renderUI({
    selectInput('questionSED', 'Select Question:',
                choices = (dtSED.subset()$strQuestion ) %>% unique(),
                #selected= "Question 43. I would recommend my department or agency as a great place to work.",
                #selected =  ( (dtSED.subset()$strQuestion ) %>% unique() )[1],
                width="100%")
  })
}

dtSED0 <- reactive({
  dtSED[strQuestion %in% input$questionSED & 
          Organization %in% input$organizationSED, 
        c(1:11, ncol(dtSED)),with=F]
})


```



### Survey Results 

```{r psesSED.plotQuestionByTime_lines}
renderPlot({
  psesSED.plotQuestionByTime_lines(dtSED0(), input$questionSED);
})
```

## Row 2 {.tabset .tabset-fade}

###  Tabulated Results {data-height=600}

<!-- ### Outputs {data-width=600} -->


```{r}
DT::renderDataTable({
  data <- dtSED0()
  DT::datatable(data, options = list(
    bPaginate = FALSE
    #    pageLength = 10
  ))
})
# renderTable({
#   dtSED0()
# })
```



### Sources


- 2018 Public Service Employee Survey Results by Theme for Science and Engineering:    
https://www.tbs-sct.gc.ca/pses-saff/2018/results-resultats/bq-pq/83/200/304/418/org-eng.aspx
- 2017 Public Service Employee Survey Results for SCIENCE AND ENGINEERING:    
https://www.tbs-sct.gc.ca/pses-saff/2017-2/results-resultats/bq-pq/83/002/022/026/org-eng.aspx
- 2014 Public Service Employee Survey Results by Question for Science and Engineering:   
https://www.tbs-sct.gc.ca/pses-saff/2014/results-resultats/bq-pq/83/001/250/255/org-eng.aspx
- 2011 Public Service Employee Survey Organizational Results: Science and Engineering:   
https://www.tbs-sct.gc.ca/pses-saff/2011/results-resultats/bq-pq/83/090/400/403/org-eng.aspx
- 2008 Public Service Employee Survey Organizational Results: Innovation, Science & Technology Branch - Laboratory & Scientific Services Directorate:    
https://www.tbs-sct.gc.ca/pses-saff/2008/results-resultats/res-eng.aspx?cd=&o1=83&o2=799&o3=702&o4=000&o5=000
 



<!-- Investigate: Track horizontally (Over time) 
# Detect:Track vertically (Over Org.Chart)  

-->


